Differentially Private Bayesian Inference

### 2018-04-23 main.tex
update

\section{Accuracy Analysis}
\subsection{Laplace Mechanism}
Fixing a data set $x$, we already had the accuracy bound based on the $l_1$ norm as:
\begin{equation*}
Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] \leq \gamma,
\end{equation*}
where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
\begin{equation*}
\begin{split}
Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[|x| ||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
& = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
& = \gamma
\end{split} 
\end{equation*}

@@

\subsection{Accuracy Study Based on $L_1$ Norm Distance}
For comparison, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig. \ref{fig_dirichlet_hellinger_l1}.

>>>>

\section{Accuracy Analysis}
\subsection{Laplace Mechanism}
Fixing a data set $x$, we already had the accuracy bound based on the $l_1$ norm as:
\begin{equation*}
Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq |x| \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] \leq \gamma,
\end{equation*}
where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
\begin{equation*}
\begin{split}
Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
& = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
& = \gamma
\end{split} 
\end{equation*}

@@

\subsection{Accuracy Study Based on $L_1$ Norm}
For comparison, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig. \ref{fig_dirichlet_hellinger_l1}.
